### 2018-06-04 Writing/draft_highlighted.tex
Finished minor corrections

Although we measured a significant difference between ``small'' and larger matrices (both in terms of number of taxa and characters; Tables \ref{Tab_pooledscharacters_test} and \ref{Tab_pooledstaxa_test}), these differences have to be contrasted with the probability of overlap between the results distributions that are always really high between every matrices sizes (Bhattacharrya Coefficients $>0.965$ for both the different number of characters and taxa).
This suggest that the effect of character correlation on recovering the right topology is independent of the size of the matrix when pooling the data.
For the number of characters, this suggests that the overall character difference metric is a good proxy for character correlation as it is independent of the number of characters analysed.
Similarly, using the a Normalised Tree Similarity metric ($NTS$) accounts for the fact that topological difference is affected by the sheer number of taxa considered (i.e. we corrected for the expected difference when comparing two random trees with the same number of taxa).

\subsection{Effect of character differences on the inference method}
When considering the pooled effect of the tree inference method, we only detected a significant difference between the Bayesian and the maximum parsimony trees in terms of clade conservation but none in terms of taxa placement (both using a Wilcoxon test and the Bhattacharrya Coefficient; Table \ref{Tab_pooledsmethods_test}).
The difference in the ability of each method to recover the ``correct'' topology has been heavily discussed in the last five years with some indications that Bayesian inference will outperform parsimony when analysing discrete morphological characters alone (\citealt{wrightbayesian2014,OReilly20160081,puttick2017uncertain}; although some critics have raised issues with these investigations \citealt{spencerefficacy2013,goloboff2017weighted}).
In this study, it is possible that our simulation protocol for generating the characters (favouring slightly more M$k$-based characters rather than HKY ones) could slightly favour Bayesian inference over maximum parsimony, however, our protocol for selecting matrices \citep[i.e. those with in a $CI<0.26$ in a quick preliminary parsimony search;][]{OReilly20160081} could also favour maximum parsimony analysis.
It was however not the purpose of this study to compare the overall performance of both methods but rather to measure the effect of character correlation on each of those methods separately.

The differences in performance of the two methods observed here could be due to the inherent mechanisms of each method.
For any given topology $T$ that was obtained from the ``normal'' matrix and a matrix with high homoplasy, both methods will generate score differently:
(1) in parsimony, the topology will probably be given a bad optimality score (on that implies many changes along the tree) and the optimality criterion (favouring the minimum score) will likely discard the tree.
The tree search will thus likely result in a topology island that will not contain the given topology $T$.
(2) in Bayesian inference, the topology will also be given a bad optimality score (i.e. low likelihood) although the high homoplasy can be accommodated in the tree through high evolution rates or/and long branches.
The rate and the branch length being two parameters among others, the optimality score (the likelihood) will change less drastically than for using parsimony.
Furthermore, in Bayesian inference, a reasonable difference in optimality between two topologies (the acceptance) will not necessarily mean that the given topology $T$ will be discarded.
This difference in both mechanisms could explain why, on average, Bayesian Inference seems better to recover the ``normal'' topology than maximum parsimony.b

\subsection{Distinction between different character correlations}
Here we mention three different types of character correlations but evolutionary biologists are mainly interested in the intra-organismal and evolutionary correlations (e.g. in evo-devo \citealt{goswami2006morphological}; or in macroevolution \citealt{fitzjohn2014much}).
These two types of correlations can only be studied \textit{a posteriori} with a phylogenetic hypothesis and should not used \textit{a priori} as a criterion to select characters.
In other words, intra-organisaml and evolutionary correlation should be studied based on an underlying phylogenetic framework making the correlation induced by data collection (i.e. coding correlation) the only type of correlation that can affect the phylogeny \textit{a priori}.
This dichotomy thus creates a trade of between: (1) coding fewer characters (stochastically reducing \textit{a priori} correlation) but making the \textit{a posteriori} correlation more dependent on the coding;
and (2) coding more characters (increasing \textit{a priori} dependence) but allowing the \textit{a posteriori} correlation being less dependent on the coding correlations.

It is important to note that the two other sources of character correlation could also be present in our simulations although they were not explicitly modelled:
(1) evolutionary correlation is implied by simulating the characters based on Birth-Death trees;
and (2) intra-organismal correlation could also be present in the matrices for those characters randomly simulated but sharing similar evolutionary simulation regimes (i.e. creating ``modules'' of characters).
However, the effect of these sources of correlation was out of the scope of this study and would have required \textit{a posteriori} changes to the matrices.% which are - when using empirical data - at best bad practice and at worth dishonest.

@@

Third, comparing phylogenetic inference methods is not trivial.
As mentioned above, both maximum parsimony and Bayesian inference, although aiming (and often achieving) to infer evolutionary history only have similar outputs and vastly differ in how optimality is measured.
But there are also difficulties in summarising both methods with consensus trees \cite{oReilly2017efficacy}.
However, we want to point out again that here we're no comparing the methods to each other \textit{per se} but rather how they both, individually, react to an increase or decrease of correlated characters.

>>>>

Although we measured a significant difference between ``small'' and larger matrices (both in terms of number of taxa and characters; Tables \ref{Tab_pooledscharacters_test} and \ref{Tab_pooledstaxa_test}), these differences have to be contrasted with the probability of overlap between the results distributions that are always \hl{very} high between every matrices sizes (Bhattacharrya Coefficients $>0.965$ for both the different number of characters and taxa).
This suggest that the effect of character correlation on recovering the right topology is independent of the size of the matrix when pooling the data.
For the number of characters, this suggests that the overall character difference metric is a good proxy for character correlation as it is independent of the number of characters analysed.
Similarly, using the Normalised Tree Similarity metric ($NTS$) accounts for the fact that topological difference is affected by the sheer number of taxa considered (i.e. we corrected for the expected difference when comparing two random trees with the same number of taxa).

\subsection{Effect of character differences on the inference method}
When considering the pooled effect of the tree inference method, we only detected a significant difference between the Bayesian and the maximum parsimony trees in terms of clade conservation but none in terms of taxa placement (both using a Wilcoxon test and the Bhattacharrya Coefficient; Table \ref{Tab_pooledsmethods_test}).
The difference in the ability of each method to recover the ``correct'' topology has been heavily discussed in the last five years with some indications that Bayesian inference will outperform parsimony when analysing discrete morphological characters alone (\citealt{wrightbayesian2014,OReilly20160081,puttick2017uncertain}; although some critics have raised issues with these investigations \citealt{spencerefficacy2013,goloboff2017weighted}).
In this study, it is possible that our simulation protocol for generating the characters (favouring slightly more M$k$-based characters rather than HKY ones) could slightly favour Bayesian inference over maximum parsimony, however, our protocol for selecting matrices \citep[i.e. those with in a $CI>0.26$ in a quick preliminary parsimony search;][]{OReilly20160081} could also favour maximum parsimony analysis.
It was however not the purpose of this study to compare the overall performance of both methods but rather to measure the effect of character correlation on each of those methods separately.

The differences in performance of the two methods observed here could be due to the inherent mechanisms of each method.
For any given topology $T$ that was obtained from the ``normal'' matrix and a matrix with high homoplasy, both methods will generate score differently:
(1) in parsimony, the topology will probably be given a bad score (one that implies many changes along the tree) and the optimality criterion (favouring the minimum score) will likely discard the tree.
The tree search will thus likely result in a topology island that will not contain the given topology $T$.
(2) in Bayesian inference, the topology will also be given a bad score (i.e. low likelihood) although the high homoplasy can be accommodated in the tree through high evolution rates or/and long branches.
The rate and the branch length being two parameters among others, the score (the likelihood) will change less drastically than for using parsimony.
Furthermore, in Bayesian inference, a reasonable difference in optimality between two topologies (the acceptance) will not necessarily mean that the given topology $T$ will be discarded.
This difference in both mechanisms could explain why, on average, Bayesian Inference seems better to recover the ``normal'' topology than maximum parsimony.

\subsection{Distinction between different character correlations}
Here we mention three different types of character correlations but evolutionary biologists are mainly interested in the intra-organismal and evolutionary correlations (e.g. in evo-devo \citealt{goswami2006morphological}; or in macroevolution \citealt{fitzjohn2014much}).
These two types of correlations can only be studied \textit{a posteriori} with a phylogenetic hypothesis and should not used \textit{a priori} as a criterion to select characters.
In other words, intra-organisaml and evolutionary correlation should be studied based on an underlying phylogenetic framework making the correlation induced by data collection (i.e. coding correlation) the only type of correlation that can affect the phylogeny \textit{a priori}.
This dichotomy thus creates a trade \hl{off} between: (1) coding fewer characters (stochastically reducing \textit{a priori} correlation) but making the \textit{a posteriori} correlation more dependent on the coding;
and (2) coding more characters (increasing \textit{a priori} dependence) but allowing the \textit{a posteriori} correlation being less dependent on the coding correlations.

It is important to note that the two other sources of character correlation could also be present in our simulations although they were not explicitly modelled:
(1) evolutionary correlation is implied by simulating the characters based on Birth-Death trees;
and (2) intra-organismal correlation could also be present in the matrices for those characters randomly simulated but sharing similar evolutionary simulation regimes (i.e. creating ``modules'' of characters).
However, the effect of these sources of correlation was out of the scope of this study and would have required \textit{a posteriori} changes to the matrices.% which are - when using empirical data - at best bad practice and at worst dishonest.

@@

Third, comparing phylogenetic inference methods is not trivial.
As mentioned above, both maximum parsimony and Bayesian inference, although aiming (and often achieving) to infer evolutionary history only have similar outputs and vastly differ in how optimality is measured.
But there are also difficulties in summarising both methods with consensus trees \cite{oReilly2017efficacy}.
% However, we want to point out again that here we're no comparing the methods to each other \textit{per se} but rather how they both, individually, react to an increase or decrease of correlated characters.
